correlationstuff

### 2024-01-15 corstuff.Rmd
commiting after a long time. oh god

---
title: "Nuclear Energy: Kahan scale and Economic Political value scale"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

# Abstract

Indian state regards nuclear energy as an important solution to rising energy needs and climate change issues. However, throughout India, nuclear power initiatives have faced opposition from people. Using survey data this study reveals that, similar to global trends, nuclear energy is perceived as highly risk in India as well. It is also perceived as the riskiest technology among all large-scale energy sources (like coal, solar, wind, oil gas, and hydro). Using risk perception theories and frameworks, this paper delves into the underlying factors influencing India's public perception of nuclear energy. While consistent demographic patterns, termed the "white male effect," influence risk perceptions in the US, demographic factors such as gender and caste have minimal influence on India's nuclear energy risk perceptions. Cultural paradigms like hierarchy versus egalitarianism and individualism versus communitarianism also show negligible impact. However, regional differences among states and economic and political values have significant impact on risk perceptions related to nuclear energy in the Indian context.

@@

# Nuclear is seen as riskier than others -this paper explore this risk perception

@@

cor(joineddf_subset_cor)

@@

#kable_table <- kable(correlation_df, caption = "Correlation Table between Perceived Risk and Perceived Benefit Variables", format = "html", #digits = 2) %>%
  #kable_styling(full_width = F) %>%
  #column_spec(1, background = "white") %>%
  #add_header_above(c(" " = 1, "Perceived Benefits" = ncol(correlation_df)))#%>%
  #pack_rows("Perceived Risks", 1, nrow(correlation_df))

# Apply alternating background colors for columns
#for (i in seq(2, ncol(correlation_df), by = 2)) {
  #kable_table <- kable_table %>%

#row_spec(i, background = "#F0F0F0")
#}

# Print the kable table
#print(kable_table)
```

@@

# Arrange plots side by side
grid.arrange(ben_plot, risky_plot, ncol=2)

@@

# H2: Gender and Caste will have significant impact like Gender and Race in the US studies of risk.

@@

alldemoslm1 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age , data = alldemos)
# Print model summary
summary(alldemoslm1)
#plot(alldemoslm1)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
alldemoslm2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = alldemos)
# Print model summary
summary(alldemoslm2)
#plot(alldemoslm1)

# most of these results indicate that there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

@@

## two linear regression models
```{r, echo=FALSE, results='asis'}
library(stargazer)

@@

# H3: Regional differences will have a strong impact

@@

#cat("\\begingroup")
#cat("\\setlength{\\tabcolsep}{1pt}")
#cat("\\renewcommand{\\arraystretch}{0.7}")
#stargazer(alldemoslm1_centered, alldemoslm2_centered, 
          #title = "Results from 2 linear regression models",
          #type = "latex"
#)
#cat("\\endgroup")

@@

## Regional Differences Graph 
Following is a graph of z scores calculated from mean perceived risk from nuclear energy by state.

```{r, echo = FALSE, fig.width=8, fig.height=4}

staterisky <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), State)

staterisky_mean <- staterisky %>%
  group_by(State) %>%
  summarise(
    Mean_Risky_Hydro = mean(Risky_Hydro, na.rm = TRUE),
    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
    Mean_Risky_Wind = mean(Risky_Wind, na.rm = TRUE),
    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE),
    Mean_Risky_Gas = mean(Risky_Gas, na.rm = TRUE),
    Mean_Risky_Oil = mean(Risky_Oil, na.rm = TRUE)
  )

# Extract only Nuclear
nuclear_data <- staterisky_mean %>%
  dplyr::select(State, Mean_Risky_Nuclear)%>%
  mutate(
    Z_Risky_Nuclear = (Mean_Risky_Nuclear - mean(Mean_Risky_Nuclear, na.rm = TRUE)) / 
                      sd(Mean_Risky_Nuclear, na.rm = TRUE)
  )

mean_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Mean_Risky_Nuclear, group = 1)) +
  geom_line(color = "#F0BA32", size = 1) +
  geom_point(color = "#F0BA32", size = 3) +
  labs(title = "Means: Perceived Risk of Nuclear Energy",
       x = "State", y = "Mean Perceived Risk") +
  theme_minimal() +
  ylim(1,5)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Plot the z-scores
zscore_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Z_Risky_Nuclear, group = 1)) +
  geom_line(color = "#F0BA32", size = 1) +
  geom_point(color = "#F0BA32", size = 3) +
  labs(title = "Z-scores: Perceived Risk of Nuclear Energy",
       x = "State", y = "Z-Score") +
  ylim(-1 ,2)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

library(gridExtra)

# Assuming mean_nuclear_state and zscore_nuclear_state are both ggplot objects

# We'll add a spacer grob for spacing between plots
spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))

grid.arrange(mean_nuclear_state, spacer, zscore_nuclear_state, ncol=3, widths=c(0.8, 0.06, 0.8))

##  kahan scale CFA, EFA and Alpha

@@

print.psych(kahan.fa, sort = TRUE)

@@

# Print the summary of the CFA results, including fit measures
#summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit
#pvalue should be greater than 0.05 p > 0.0.5

# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian. Again we see that individualistic variables just don't fit here.

# creating table of factor scores

@@

## RMSEA is still pretty big.

@@

@@

# EDIT : Scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales

```{r dev = "jpg", echo=FALSE}

#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.

Kscalescores %>%
  ggplot(aes(Communitarianism_score,Egalitarianism_score))+
  geom_count(aes(color = ..n.., size = ..n..))+
  guides(color = 'legend')+
  geom_hline(yintercept=3, colour="black", lwd=1)+
  geom_vline(xintercept=3.5, colour="black", lwd=1)+
  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
  ylim(2,6)+
  xlim(2,6)+
  theme_minimal()

@@

# all lms after FA
```{r, echo=FALSE}
# 3 linear models - 1) lm with demographic variables except age and State
m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)
# Print model summary
#summary(m1_demo)
#plot(m1_demo)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
m2_demo<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores)
# Print model summary
#summary(m2_demo)
#plot(m2_demo)

# States and some age have some impact on y variable.

# 3) lm with kahan 
m1_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = fascale_scores)
# Print model summary
summary(m1_kahan)
#plot(m1_kahan)

# 4) lm with ecopolvars 
m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)
# Print model summary
summary(m1_allscales)
#plot(m1_allscales)

@@

# binding ecopol with alternative Kahan scale score 
fascale_scores2 <-cbind(Kscalescores, scores1)  %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2)

@@

@@

# graphs for lm attempts

library(interactions)
sim_slopes(m1_allscales2, pred = Ndevelop, modx = State)

ggplot(fascale_scores, aes(x = Ndevelop, y = Risky_Nuclear, color = State)) +
  geom_point(alpha = 0.5) +  # Add points with some transparency
  geom_smooth(method = 'lm', se = FALSE) +  # Add linear regression lines
  theme_minimal() +
  labs(title = "Interaction Plot",
       x = "National Development (Ndevelop)",
       y = "Perceived Risk (Risky_Nuclear)")
library(car)
vif(m1_allscales)

str(fascale_scores)

ggplot(fascale_scores, aes(x = Pdevelop, y = Risky_Nuclear)) +
  geom_point() +  # or geom_line() depending on how you want to visualize it
  facet_wrap(~ State) +  # This will create separate plots for each State
  labs(title = "Risky Nuclear vs Pdevelop by State",
       x = "Pdevelop",
       y = "Risky Nuclear") +
  theme_minimal()

ggplot(fascale_scores, aes(x = Ndevelop, y = Risky_Nuclear)) +
  geom_jitter(alpha = 0.5, width = 0.2) +
  #facet_wrap(~ State) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Relationship between Ndevelop and Risky Nuclear",
       x = "Ndevelop",
       y = "Risky Nuclear") +
  theme_minimal()

ggplot(fascale_scores, aes(x = Pdevelop, y = Risky_Nuclear)) +
  geom_jitter(alpha = 0.5, width = 0.2) +
  facet_wrap(~ State) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Relationship between Ndevelop and Risky Nuclear",
       x = "Ndevelop",
       y = "Risky Nuclear") +
  theme_minimal()

ggplot(fascale_scores, aes(x = State, y = Risky_Nuclear)) +
  geom_boxplot() +
  #facet_wrap(~ State) +
  theme_minimal()
```

@@

# H4 : Economic and Political Values will be important in explaining perceived risk from Nuclear Energy

@@

@@

# Logistic Regression

```{r, echo=FALSE}
library(MASS)

fascale_scores1 <- fascale_scores %>%
  mutate_at(vars(Risky_Nuclear), as.factor)

## one at a time, table 
#lapply(fascale_scores1[, c("Risky_Nuclear", "Uppercaste", "Male", "Hindu","Urban", "State") ], table)
## three way cross tabs (xtabs) and flatten the table
#ftable(xtabs(~ Uppercaste + Risky_Nuclear + Male, data = fascale_scores1))
## three way cross tabs (xtabs) and flatten the table
#ftable(xtabs(~ State + Risky_Nuclear + Urban, data = fascale_scores1))

logm1= polr(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +age + KahanS + KahanH + Pdevelop + Ndevelop + State  , data = fascale_scores1, Hess = TRUE)
#summary(logm1)

ctable1 <- coef(summary(logm1))

## calculate and store p values
p1 <- pnorm(abs(ctable1[, "t value"]), lower.tail = FALSE) * 2

## combined table
ctable1 <- cbind(ctable1, "p value" = round(p1,3))

pvalue <- as_tibble(ctable1) %>%
  dplyr::select("p value")%>%
  slice(1:(n() - 4))

ci <- confint(logm1)# default method gives profiled CIs

#confint.default(logm1) # CIs assuming normality

## odds ratios
#exp(coef(logm1))

## OR and CI
ORtable <- cbind("Odds Ratio" = coef(logm1), ci, pvalue) %>%
  mutate(
    `Odds Ratio` = round(`Odds Ratio`, 3),
    `2.5 %` = round(`2.5 %`, 3),
    `97.5 %` = round(`97.5 %`, 3)
  )

ORtableout <- knitr::kable(ORtable, booktabs = TRUE, caption = "Odds Ratio for Perceived Risk from Nuclear Energy") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

ORtableout

@@

```{r, echo=FALSE}
# Q7 : political values scale - factor analysis - reduce dimensions and then run regression -logistic regression 
# Using logistic regression for the SYSTEM prefixed variables.

#codedmodule2
#codedmodule2$SYSTEMDEMO <- as.factor(codedmodule2$SYSTEMDEMO)
#levels(codedmodule2$SYSTEMDEMO)

#codedmodule2$SYSTEMRELIGION <- as.factor(codedmodule2$SYSTEMRELIGION)
#levels(codedmodule2$SYSTEMRELIGION)

#codedmodule2$SYSTEMTOTAL <- as.factor(codedmodule2$SYSTEMTOTAL)
#levels(codedmodule2$SYSTEMTOTAL)

#codedmodule2$SYSTEMTECHNO <- as.factor(codedmodule2$SYSTEMTECHNO)
#levels(codedmodule2$SYSTEMTECHNO)

#codedmodule2$Risky_Nuclear <- as.factor(codedmodule2$Risky_Nuclear)
#levels(codedmodule2$Risky_Nuclear)

#fitrisky_nucleargm <- with(codedmodule2, clm(Risky_Nuclear ~ 1 + SYSTEMDEMO + SYSTEMRELIGION + SYSTEMTOTAL + SYSTEMTECHNO))

@@

```{r, echo =FALSE}

# same things with benefit from Nuclear Energy
fascalesben <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Ben_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()

# Run CFA
Kahan_cfaben <- cfa(Kahan_fas, data = fascalesben, std.lv = TRUE)

Kahan_scoresben <- predict(Kahan_cfaben, newdata = fascalesben)

Kahan_Kscoresben <- cbind(fascalesben, Kahan_scoresben)

ecopolallben <- fascalesben %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")

ecopolallben_alpha <- psych::alpha(ecopolallben, check.keys = TRUE)

ecopolallben_cor <- cor(ecopolallben)
PCA24 <- principal(ecopolallben, nfactors = 24, rotate = "none") # no rotation to start with.

ecopolallben2.fa <- fa(ecopolallben, nfactors = 2, rotate = "varimax")

ecopolallben_scores <- psych::factor.scores(ecopolallben, ecopolallben2.fa)

# The factor scores will be stored in the scores element of the returned list
scores2 <- ecopolallben_scores$scores

fascale_scoresben <- cbind(Kahan_Kscoresben, scores2) %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2) #%>%
  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))

mbennuclear <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop , data = fascale_scoresben)
# Print model summary
#summary(mbennuclear)

# Appendix: Characteristics of the Sample

The following graph shows that distribution of different demographic variables in our sample of 2,160 from the combined dataset from both surveys.
The percentages are rounded off to whole numbers.

library(dplyr)
library(tidyr)

sampledemos <- joineddf1 %>% 
  dplyr::select("State", "Language", "age", "urban_rural", "gender", "caste" ,"religion") %>%
              mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
              mutate_all(~ifelse(. == "OBC", "Other Backward Classes (OBC)", .))%>%
              mutate_all(~ifelse(. == "SC", "Scheduled caste (SC)", .))%>%
              mutate_all(~ifelse(. == "ST", "Scheduled tribe (ST)", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "TA", "Tamil", .)) %>%
              mutate_all(~ifelse(. == "EN", "English", .))%>%
              mutate_all(~ifelse(. == "BN", "Bengali", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "HI", "Hindi", .))%>%
              na.omit()

#changing factor levels for each variable from high to low n

sampledemos$State <- factor(sampledemos$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
sampledemos$Language <- factor(sampledemos$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
sampledemos$age <- factor(sampledemos$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
sampledemos$urban_rural <- factor(sampledemos$urban_rural, levels = c("Rural","Urban"))
sampledemos$gender <- factor(sampledemos$gender, levels = c("Male","Female"))
sampledemos$caste <- factor(sampledemos$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
sampledemos$religion <- factor(sampledemos$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))

```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}

# Loading the required libraries
library(tidyverse)
library(gridExtra)
library(scales)

# Function to create bar plot
create_bar_plot <- function(data, variable_name, palette_name) {
  factor_levels <- levels(sampledemos[[variable_name]])
  data %>%
    filter(Variable == variable_name) %>%
    mutate(Category = factor(Category, levels = factor_levels)) %>%
    ggplot(aes(y = "", x = Percentage, fill = Category)) +
    geom_bar(position = "fill", stat = "identity", width = 1) +
    geom_text(aes(label = paste0(round(Percentage, 0), "%")), 
              position =  position_fill(vjust = 0.5)) +
    scale_x_continuous(labels = percent) +
    labs(y = NULL, x = "Percentage", fill = variable_name) +
    theme_classic() +
    theme(axis.text.y = element_blank(), strip.text = element_text(size = 10), legend.position = "top") +
    scale_fill_brewer(palette = palette_name)
}

# Gather data to long format and calculate counts and percentages
df_barplot <- sampledemos %>%
  gather(Variable, Category) %>%
  group_by(Variable, Category) %>%
  filter(!is.na(Category)) %>%
  summarise(n = n()) %>%
  mutate(Percentage = n / sum(n) * 100)

# Create separate plots for each variable
plot_state <- create_bar_plot(df_barplot, "State", "Spectral")
plot_language <- create_bar_plot(df_barplot, "Language", "Paired")
plot_age <- create_bar_plot(df_barplot, "age", "Set3")
plot_urban_rural <- create_bar_plot(df_barplot, "urban_rural", "Dark2")
plot_gender <- create_bar_plot(df_barplot, "gender", "Pastel1")
plot_caste <- create_bar_plot(df_barplot, "caste", "Set1")
plot_religion <- create_bar_plot(df_barplot, "religion", "Set2")

# Combine the plots with spacing
combined_plot <- gridExtra::arrangeGrob(plot_state, plot_language, plot_age, plot_urban_rural, plot_gender, plot_caste, plot_religion, ncol = 1, heights = c(1, 1, 1, 1, 1, 1, 1))

# Print the combined plot
grid::grid.newpage()
grid::grid.draw(combined_plot)

>>>>

---
title: "correlationstuff"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

@@

@@

#cor(joineddf_subset_cor)

@@

@@

# Arrange plots side by side
#grid.arrange(ben_plot, risky_plot, ncol=2)

@@

@@

alldemoslm1 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age , data = alldemos)
# Print model summary
#summary(alldemoslm1)
#plot(alldemoslm1)

# 2) lm with all demographic variables
alldemoslm2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = alldemos)
# Print model summary
#summary(alldemoslm2)
#plot(alldemoslm1)

@@

## Demographic IVs - two linear regression models
```{r, echo=FALSE, results='asis'}
library(stargazer)

@@

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(alldemoslm1_centered, alldemoslm2_centered, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

@@

##  Kahan scale Alpha values 
Hierarchy - Egalitarianism scale alpha  =  0.7
Individualism - Communitarianism scale alpha= 0.52
Only Individualism scale alpha = 0.31 
Only Communitarianism scale alpha = 0.72

@@

@@

@@

@@

# EDIT :  Kahan scale EFA  
```{r, echo=FALSE}

#print.psych(kahan.fa, cut = 0.4, sort = TRUE)

rename_map <- c(
  "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
  "K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
  "K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
  "K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
  "K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women."
)

fa_table(kahan.fa) %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("Kahan Exploratory Factor Analysis Table")

@@

@@

# all lms after FA
```{r, echo=FALSE}
# 3 linear models - 1) lm with demographic variables except age and State
m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)

# 2) lm with all demographic variables
m2_demo<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores)

# 3) lm with kahan 
m1_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = fascale_scores)

# 4) lm with ecopolvars 
m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)

@@

# Correlation Eco-pol and alt Kahan(mean across)

```{r}
# binding ecopol with alternative Kahan scale score 
fascale_scores2 <-cbind(Kscalescores, scores1)  %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2)

@@

print(cor_kecopol)
```

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(m1_kahan2, m1_ecopol2, m1_allscales2, 
          title = "Results from 3 linear regression models",
          type = "latex"
)
cat("\\endgroup")

@@

# LMs : eco-pol and kahan scale

@@

\newpage
```{r, echo=FALSE, results='asis'}
library(stargazer)

@@

# LMs by State

fascale_scores

# make state wise dts

# Uttar Pradesh
UP<- fascale_scores %>%
  filter(State == "Uttar Pradesh")

Raj<- fascale_scores %>%
  filter(State == "Rajasthan")

TM<- fascale_scores %>%
  filter(State == "Tamil Nadu")

Mah<- fascale_scores %>%
  filter(State == "Maharasthra")

Bengal <- fascale_scores %>%
  filter(State == "Bengal")

# 3 linear models - 1) lm with demographic variables except age and State
TM_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = TM)

# 3) lm with kahan 
TM1_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age  + KahanS + KahanH , data = TM)

# 4) lm with ecopolvars 
TM1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + Pdevelop + Ndevelop + KahanS + KahanH , data = TM)

TM1_ecopol <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age +  Pdevelop + Ndevelop,  data = TM)

summary(TM1_ecopol)

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(TM_demo, TM1_kahan, TM1_allscales, TM1_ecopol,
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

@@
